---
title: "heatwave analysis for the finer grid"
author: "Yujie Xu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/AH_LA_AnalysisPaper/rmd/")
```

```{r helpers, message=FALSE}
library("dplyr")
library("tmap")
library("ggpmisc")
```

# Environment variables before and after the heatwave

```{r plotEnvrn, message=FALSE}
devtools::load_all("../AH.Analysis")

df.weather.2018 %>%
  dplyr::mutate(cell.id = factor(cell.id)) %>%
  dplyr::filter((month == 6 & day > 26) | (month == 7 & day < 15)) %>%
  dplyr::select(cell.id, month:minute, DryBulb.C, RelHum.percent, `WindSpd.m/s`
                ) %>%
  dplyr::mutate(timestamp = sprintf("2018-%02d-%02d %02d:%02d:00", month, day, hour, minute)) %>%
  dplyr::mutate(timestamp.pox = as.POSIXct(timestamp)) %>%
  tidyr::gather(variable, value, DryBulb.C:`WindSpd.m/s`) %>%
  dplyr::mutate_at(vars(variable), recode, "DryBulb.C"="Dry Bulb Temperature (C)",
                   "RelHum.percent" = "Relative Humidity (%)",
                   "WindSpd.m/s"="Wind Speed (m/s)") %>%
  ggplot2::ggplot(ggplot2::aes(x=timestamp.pox, y=value, color=cell.id, group=cell.id)) +
  ggplot2::geom_line(size = 0.2) +
  ggplot2::facet_wrap(.~variable, ncol=1, scales = "free_y") +
  ggplot2::geom_vline(xintercept = c(as.POSIXct("2018-06-29 00:00:00"),
                                     as.POSIXct("2018-07-06 00:00:00"),
                                     as.POSIXct("2018-07-13 00:00:00")), linetype = "dashed") +
  ggplot2::xlab("Time") +
  ggplot2::ylab("") +
  ggplot2::theme()
ggplot2::ggsave("../images/heatwave_weather.png", width = 10, height = 5)

coastal.cells = c(9, 23, 36, 35, 34)
inland.cells = c(65, 66, 79, 68, 120)

df.weather.2018 %>%
  dplyr::filter(cell.id %in% c(coastal.cells, inland.cells)) %>%
  dplyr::mutate(location = ifelse(cell.id %in% coastal.cells, "coastal", "inland")) %>%
  ## dplyr::mutate(cell.id = factor(cell.id)) %>%
  dplyr::filter((month == 6 & day > 26) | (month == 7 & day < 15)) %>%
  dplyr::select(cell.id, location, month:minute, DryBulb.C, RelHum.percent, `WindSpd.m/s`
                ) %>%
  dplyr::mutate(timestamp = sprintf("2018-%02d-%02d %02d:%02d:00", month, day, hour, minute)) %>%
  dplyr::mutate(timestamp.pox = as.POSIXct(timestamp)) %>%
  tidyr::gather(variable, value, DryBulb.C:`WindSpd.m/s`) %>%
  dplyr::mutate_at(vars(variable), recode, "DryBulb.C"="Dry Bulb Temperature (C)",
                   "RelHum.percent" = "Relative Humidity (%)",
                   "WindSpd.m/s"="Wind Speed (m/s)") %>%
  ggplot2::ggplot(ggplot2::aes(x=timestamp.pox, y=value, color=location, group=cell.id)) +
  ggplot2::geom_line(size = 0.2) +
  ggplot2::facet_wrap(.~variable, ncol=1, scales = "free_y") +
  ggplot2::geom_vline(xintercept = c(as.POSIXct("2018-06-29 00:00:00"),
                                     as.POSIXct("2018-07-06 00:00:00"),
                                     as.POSIXct("2018-07-13 00:00:00")), linetype = "dashed") +
  ggplot2::xlab("Time") +
  ggplot2::ylab("") +
  ggplot2::theme()
ggplot2::ggsave("../images/heatwave_weather_inland_coastal.png", width = 10, height = 5)
```

# Hourly AH timeseries by component

```{r plotAHtimeSeries}

grid.area = grid.finer %>%
  dplyr::select(id.grid.finer, FootprintArea.m2)

sf::st_geometry(grid.area) <- NULL

to.plot.quartile <- hourly.AH.per.to.during.heatwave.finer %>%
  dplyr::mutate(emission.exf.exhaust.relief = emission.exfiltration + emission.exhaust + emission.ref) %>%
  dplyr::select(-emission.exfiltration, -emission.exhaust, -emission.ref) %>%
  dplyr::select(geoid:hour, status, everything()) %>%
  tidyr::gather(variable, value, emission.rej:emission.exf.exhaust.relief) %>%
  dplyr::left_join(grid.area, by = c("geoid"="id.grid.finer")) %>%
  dplyr::mutate(value = value * 0.000277778 / FootprintArea.m2) %>%
  dplyr::group_by(date, hour, status, variable) %>%
  dplyr::summarise_at(vars(value),
                      tibble::lst(
                                  "25th"=~quantile(., probs=0.25),
                                  "50th"=~quantile(., probs=0.5),
                                  "75th"=~quantile(., probs=0.75)
                                  )) %>%
  dplyr::ungroup() %>%
  tidyr::gather(percentile, value, ends_with("th")) %>%
  dplyr::mutate_at(vars(variable), recode, "emission.overall"="overall heat emission", "emission.exf.exhaust.relief"="zone exfiltration + exhaust + relief air", "emission.rej"="HVAC heat rejection", "emission.surf"="surface heat emission") %>%
  dplyr::mutate(datetime = as.POSIXct(sprintf("2018/%s %s", date, hour), format="%Y/%m/%d %H:%M:%S")) %>%
  dplyr::mutate(variable = factor(variable,
                                  levels = c("HVAC heat rejection",
                                             "zone exfiltration + exhaust + relief air",
                                             "surface heat emission",
                                             "overall heat emission"))) %>%
  {.}

to.plot.quartile %>%
  ggplot2::ggplot(ggplot2::aes(x=datetime, y=value, color=percentile,
                               group=interaction(variable, percentile))) +
  ggplot2::geom_path(size=0.2) +
  ggplot2::ggtitle("Distribution of hourly heat emission at 450m wide WRF grid resolution") +
  ggplot2::ylab("Wh/m2 building footprint area") +
  ggplot2::geom_vline(xintercept = c(as.POSIXct("2018-06-29 00:00:00"),
                                     as.POSIXct("2018-07-06 00:00:00"),
                                     as.POSIXct("2018-07-13 00:00:00")), linetype = "dashed") +
  ggplot2::facet_wrap(.~variable, ncol=1) +
  ggplot2::theme()
ggplot2::ggsave("../images/building_quartile_emission_Wperm2.png", width = 7, height=5, dpi=600)
```

# Before vs after heatwave heat emission change
## Total AH

```{r AHchange, message=FALSE}

heatwave.days = sprintf("07/%02d", 6:12)

pre.heatwave.days = c(sprintf("06/%02d", 29:30), sprintf("07/%02d", 1:5))

weekly.total.pre.vs.within.heatwave <- df.finer.daily %>%
  dplyr::filter(date %in% c(pre.heatwave.days, heatwave.days)) %>%
  dplyr::select(-starts_with("energy")) %>%
  dplyr::mutate(emission.overall.no.surf = emission.overall - emission.surf) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:emission.overall.no.surf) %>%
  dplyr::mutate(status = ifelse(date %in% heatwave.days, "heatwave", "pre-heatwave")) %>%
  dplyr::group_by(geoid, status, variable) %>%
  dplyr::summarise(GJ = sum(GJ)) %>%
  dplyr::ungroup() %>%
  tidyr::spread(status, GJ) %>%
  dplyr::mutate(weekly.total.diff.GJ = heatwave - `pre-heatwave`) %>%
  {.}

variable.label = tibble::tibble(variable = c("emission.surf", "emission.rej", "emission.exfiltration", "emission.exhaust", "emission.ref", "emission.overall", "emission.overall.no.surf"),
                                component = c("Surface convection",
                                              "HVAC rejection", "Exfiltration",
                                              "Exhaust air", "HVAC Relief air",
                                              "Total",
                                              "non-surface Total"))

dfs.by.variable <- weekly.total.pre.vs.within.heatwave %>%
  dplyr::left_join(variable.label, by = "variable") %>%
  dplyr::group_by(variable) %>%
  dplyr::group_split()

ttest.result <- lapply(dfs.by.variable, function(df.i) {
  var.name = df.i$variable[[1]]
  var.label = df.i$component[[1]]
  out <- t.test(df.i$weekly.total.diff.GJ)
  tibble::tibble(variable = var.name, mean = out$estimate[[1]], ci.low = out$conf.int[[1]], ci.hi = out$conf.int[[2]], p.value = out$p.value[[1]], component = var.label)
}) %>%
  dplyr::bind_rows()

variable.order = tibble::tibble(order = 1:7, variable = c("emission.surf", "emission.rej", "emission.exfiltration", "emission.exhaust", "emission.ref", "emission.overall", "emission.overall.no.surf"))

ttest.result.tbl <- ttest.result %>%
  dplyr::left_join(variable.order, by = "variable") %>%
  dplyr::arrange(order) %>%
  dplyr::select(component, mean, ci.low, ci.hi, p.value) %>%
  {.}

ttest.result.tbl %>%
  knitr::kable()

ttest.result.tbl %>%
  readr::write_csv("../table/AH_change_by_component_ttest.csv")

plot.ttest.result <- function(result.tbl, imagefile, dashline.pos) {
  result.tbl %>%
    ggplot2::ggplot(ggplot2::aes(x = component, y = mean)) +
    ggplot2::geom_point(stat = "identity") +
    ggplot2::geom_errorbar(ggplot2::aes(ymin = ci.low, ymax = ci.hi), width = 0.3) +
    ggplot2::theme_bw() +
    ggplot2::ggtitle("Average change in AH during the heatwave week vs one week before (GJ)") +
    ggplot2::ylab("Change in AH (GJ)") +
    ggplot2::xlab("AH component") +
    ggplot2::geom_hline(yintercept = 0) +
    ggplot2::geom_vline(xintercept = dashline.pos, linetype = "dashed") +
    ggplot2::coord_flip() +
    ggplot2::theme()
  ggplot2::ggsave(sprintf("../images/%s", imagefile), width = 8.5, height = 3)
}

ttest.result.tbl %>%
  dplyr::filter(!component %in% c("Total", "Surface convection")) %>%
  plot.ttest.result("AH_change_pre_to_within_heatwave_no_surf.png", 4.5)

ttest.result.tbl %>%
  dplyr::mutate(component = factor(component, levels = c("Surface convection", "HVAC rejection", "Exfiltration", "Exhaust air", "HVAC Relief air", "Total", "non-surface Total"))) %>%
  plot.ttest.result("AH_change_pre_to_within_heatwave.png", 5.5)
```

# Spatial pattern of the AH increaser vs decreasers

```{r mapAHchange, message = FALSE}

for (i in seq_along(dfs.by.variable)) {
  var.name = dfs.by.variable[[i]]$variable[[1]]
  var.label = dfs.by.variable[[i]]$component[[1]]
  print(var.name)
  print(var.label)
  to.plot <- dfs.by.variable[[i]] %>%
    dplyr::mutate(change = ifelse(weekly.total.diff.GJ > 0, "increase", "decrease")) %>%
    dplyr::left_join(grid.finer, by = c("geoid"="id.grid.finer")) %>%
    sf::st_as_sf() %>%
    {.}
  if (i != 6) {
    p <- tm_shape(to.plot) +
      tm_polygons(col="change", border.alpha = 0, palette = "Set2") +
      tm_layout(main.title = sprintf("pre-to-during heatwave change in\n%s AH(GJ)", var.label),
                legend.position=c("left", "bottom"), legend.outside=FALSE) +
      tm_shape(la.boundary.valid) +
      tm_polygons("CITY", alpha=0, legend.show=FALSE)
  } else {
    p <- tm_shape(to.plot) +
      tm_polygons(col="change", border.alpha = 0, palette = "#FC8D62") +
      tm_layout(main.title = sprintf("pre-to-during heatwave change in\n%s AH(GJ)", var.label),
                aes.palette = list(seq = "-Set2"),
                legend.position=c("left", "bottom"), legend.outside=FALSE) +
      tm_shape(la.boundary.valid) +
      tm_polygons("CITY", alpha=0, legend.show=FALSE)
  }
  tmap_save(p, sprintf("../images/pre-to-during_AH_change_%s.png", gsub(".", "_", var.name, fixed=TRUE)))
}
```

# Prototype building model pre-to-during heatwave AH change

```{r preVsDuringByType, message = FALSE}
idf.epw.AH.pre.during.heatwave.diff <- epout.pre.during.heatwave %>%
  dplyr::select(-starts_with("energy")) %>%
  dplyr::mutate(emission.overall.no.surf = emission.overall - emission.surf) %>%
  dplyr::mutate(status = ifelse(date %in% heatwave.days, "heatwave", "pre-heatwave")) %>%
  dplyr::group_by(idf.kw, epw.id, building.type, vintage, status) %>%
  dplyr::summarise_if(is.numeric, sum) %>%
  dplyr::ungroup() %>%
  tidyr::gather(variable, value, emission.exfiltration:emission.overall.no.surf) %>%
  ## convert to MJ
  dplyr::mutate(value = value * 1e-6) %>%
  dplyr::left_join(prototype.area, by = "idf.kw") %>%
  ## convert to MJ/m2
  dplyr::mutate(value = value / prototype.m2) %>%
  tidyr::spread(status, value) %>%
  dplyr::mutate(weekly.total.diff.MJ.per.m2 = heatwave - `pre-heatwave`) %>%
  {.}

idf.epw.AH.pre.during.heatwave.diff <- idf.epw.AH.pre.during.heatwave.diff %>%
  dplyr::mutate(sector = ifelse(building.type %in% c("single-family", "multi-family"), "residential", "non-residential")) %>%
  dplyr::left_join(variable.label, by = "variable") %>%
  {.}

plot.pre.to.during.hw.AH.by.type <- function(df, image.height = 4, sector.filter=NULL) {
  var.name = df$variable[[1]]
  var.label = df$component[[1]]
  if (!is.null(sector.filter)) {
    to.plot <- df %>%
      dplyr::filter(sector == sector.filter)
    imagename = sprintf("../images/%s_change_pre_to_within_heatwave_epout_%s.png", gsub(".", "_", var.name, fixed=TRUE), sector.filter)
    titlestr = sprintf("Pre-to-during heatwave %s change for prototype buildings\n(%s buildings)", var.label, sector.filter)
  } else {
    to.plot <- df
    imagename = sprintf("../images/%s_change_pre_to_within_heatwave_epout.png", gsub(".", "_", var.name, fixed=TRUE))
    titlestr = sprintf("Pre-to-during heatwave %s change for prototype buildings", var.label)
  }
  to.plot %>%
    dplyr::select(-epw.id, -prototype.m2, -heatwave, -`pre-heatwave`) %>%
    dplyr::group_by(idf.kw, building.type, vintage, variable) %>%
    dplyr::summarise_at(vars(weekly.total.diff.MJ.per.m2), tibble::lst(min, mean, max)) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(vintage = factor(vintage, levels = c("before 1980", "1981-2008 (2004)", "after 2008 (2013)"))) %>%
    ggplot2::ggplot(ggplot2::aes(x = building.type, y = mean)) +
    ggplot2::geom_point(size = 0.7) +
    ggplot2::geom_errorbar(ggplot2::aes(ymin = min, ymax = max), width = 0.3, size = 0.2) +
    ggplot2::facet_wrap(.~vintage, nrow = 1) +
    ggplot2::coord_flip() +
    ggplot2::geom_hline(yintercept = 0, linetype = "dashed") +
    ggplot2::ggtitle(titlestr) +
    ggplot2::ylab("MJ/m2 building size") +
    ggplot2::theme()
  ggplot2::ggsave(imagename, width = 8.5, height = image.height)
}

dfs.prototype.results <- idf.epw.AH.pre.during.heatwave.diff %>%
  dplyr::group_by(variable) %>%
  dplyr::group_split()

for (df in dfs.prototype.results) {
  plot.pre.to.during.hw.AH.by.type(df, image.height = 2.5, sector.filter = "residential")
  plot.pre.to.during.hw.AH.by.type(df, image.height = 4, sector.filter = "non-residential")
}

```

# Linear regression fit coarse grid

Daily AH and daily average temperature regression. Averaged over grid cells.

```{r linReg}

heatwave.days = sprintf("07/%02d", 6:12)
pre.heatwave.days = c(sprintf("06/%02d", 29:30), sprintf("07/%02d", 1:5))

daily.avg.temperature <- df.weather.2018 %>%
  dplyr::group_by(cell.id, year, month, day) %>%
  dplyr::summarize(DryBulb.C = mean(DryBulb.C)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(date = sprintf("%02d/%02d", month, day)) %>%
  dplyr::select(cell.id, date, DryBulb.C)

grid.finer.centroid = sf::st_centroid(grid.finer)

finer.to.coarse.mapping <- sf::st_join(grid.coarse %>% select(id.grid.coarse), grid.finer.centroid %>% select(id.grid.finer), join = sf::st_contains)

sf::st_geometry(finer.to.coarse.mapping) <- NULL

finer.to.coarse.mapping <- finer.to.coarse.mapping %>%
  tibble::as_tibble()

dfs.to.plot <- df.finer.daily %>%
  dplyr::left_join(finer.to.coarse.mapping, by = c("geoid"="id.grid.finer")) %>%
  dplyr::left_join(daily.avg.temperature, by = c("id.grid.coarse"="cell.id", "date")) %>%
  dplyr::select(-starts_with("energy")) %>%
  tidyr::gather(variable, GJ, starts_with("emission")) %>%
  dplyr::group_by(date, variable) %>%
  dplyr::summarize_at(vars(DryBulb.C, GJ), mean) %>%
  dplyr::left_join(variable.label, by = "variable") %>%
  dplyr::group_by(variable) %>%
  dplyr::group_split() %>%
  {.}

dfs.to.plot[[1]]

plot.scatter.cmp <- function(df, title.str, output.name) {
  p <- df %>%
    ggplot2::ggplot(ggplot2::aes(x=`DryBulb.C`, y=`GJ`)) +
    ggplot2::geom_point(size = 0.2) +
    ggpmisc::stat_poly_line(formula = y ~ x) +
    ggpmisc::stat_poly_eq(formula = y ~ x, aes(label = paste(after_stat(eq.label),
                                                                  after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::ggtitle(title.str) +
    ggplot2::xlab("average daily temperature (°C)") +
    ggplot2::ylab("GJ") +
    ggplot2::theme()
  print(p)
  ggplot2::ggsave(output.name, width = 6, height = 4, dpi = 600)
}

## restrict to july
for (i in seq_along(dfs.to.plot)) {
  df.i = dfs.to.plot[[i]] %>%
    ## restrict to july
    tidyr::separate(date, into = c("month", "day"), sep = "/", remove = FALSE) %>%
    dplyr::filter(month == "07") %>%
    dplyr::select(-month, -day) %>%
    {.}
  title.str = sprintf("Daily %s AH - daily average temperature, 2018 Jul", df.i$component[[1]])
  var.name = df.i$variable[[1]]
  output.name = sprintf("../images/jul_AH_temperature_%s.png", gsub(".", "_", var.name, fixed = TRUE))
  plot.scatter.cmp(df.i, title.str, output.name)
}

## all year
for (i in seq_along(dfs.to.plot)) {
  df.i = dfs.to.plot[[i]]
  title.str = sprintf("Daily %s AH - daily average temperature, 2018", df.i$component[[1]])
  var.name = df.i$variable[[1]]
  output.name = sprintf("../images/AH_temperature_%s.png", gsub(".", "_", var.name, fixed = TRUE))
  plot.scatter.cmp(df.i, title.str, output.name)
}
```

# Map view of different timestep of a heatwave day

```{r hourMap}
dfs.to.plot.map <- hourly.AH.per.to.during.heatwave.finer %>%
  dplyr::mutate(hour = as.numeric(substr(hour, 1, 2)) - 1) %>%
  dplyr::filter(date == "07/06", hour %in% c(0, 6, 12, 18)) %>%
  dplyr::select(-status) %>%
  tidyr::gather(variable, J, emission.exfiltration:emission.overall) %>%
  dplyr::left_join(variable.label, by = "variable") %>%
  dplyr::filter(variable %in% c("emission.overall", "emission.rej", "emission.surf")) %>%
  dplyr::group_by(variable) %>%
  dplyr::group_split() %>%
  {.}

for (df.j in dfs.to.plot.map) {
  var.name = df.j$variable[[1]]
  title.str = sprintf("%s AH snapshot (Jul. 6, 2018)", df.j$component[[1]])
  output.name = sprintf("../images/snapshot_0706_%s.png", gsub(".", "_", var.name, fixed = TRUE))
  print(title.str)
  to.plot.j <- df.j %>%
    dplyr::left_join(grid.finer %>% dplyr::select(id.grid.finer, FootprintArea.m2),
                     by = c("geoid"="id.grid.finer")) %>%
    ## convert to w/m2
    dplyr::mutate(w.per.m2 = J * 0.000277778 / FootprintArea.m2) %>%
    sf::st_as_sf() %>%
    {.}
  p <- tm_shape(to.plot.j) +
    tm_polygons(col="w.per.m2", n=8, style="quantile", midpoint=0, palette = "seq", border.alpha = 0) +
    tm_facets(by="hour", ncol=4) +
    tm_layout(main.title = title.str,
              legend.position=c("left", "bottom"), legend.outside=FALSE,
              aes.palette = list(seq = "-RdYlGn")) +
    tm_shape(la.boundary.valid) +
    tm_polygons("CITY", alpha=0, legend.show=FALSE)
  print(p)
  tmap_save(p, output.name, width=12, height=4)
}
```

# July total heat emission by prototype building
```{r barPlot}

jul.sim.EUI.avg <- mon.sim.result.by.idf.epw %>%
  dplyr::filter(month == "07") %>%
  dplyr::select(-epw.id) %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  dplyr::select(idf.kw, emission.overall, energy.overall) %>%
  dplyr::left_join(prototype.area, by = "idf.kw") %>%
  dplyr::mutate(EUI.GJ.per.m2 =  energy.overall * 1e-9 / prototype.m2) %>%
  dplyr::mutate(emission.GJ.per.m2 =  emission.overall * 1e-9 / prototype.m2) %>%
  dplyr::select(idf.kw, EUI.GJ.per.m2, emission.GJ.per.m2) %>%
  tidyr::gather(variable, value, ends_with("per.m2")) %>%
  {.}

jul.sim.EUI.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  dplyr::mutate_at(vars(variable), recode, "EUI.GJ.per.m2"="Electricity + Gas GJ/m2",
                   "emission.GJ.per.m2"="Heat Emission GJ/m2") %>%
  na.omit() %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, value), y=value, fill=interaction(variable, usetype))) +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ## ggplot2::scale_fill_grey(start=0.8, end=0.2) +
  ggplot2::scale_fill_brewer(palette = "Paired", direction=-1, name = "") +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=4)) +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::ggtitle("Prototype building annual energy and heat emission") +
  ggplot2::coord_flip() +
  ggplot2::theme(legend.position = "bottom")
ggplot2::ggsave(sprintf("../images/jul_energy_heat_prototype.png"), width = 9, height = 10)


```

# July heat emission to energy ratio

```{r barHeatOverEnergy}
heat.eui.ratio <- mon.sim.result.by.idf.epw %>%
    dplyr::filter(month == "07") %>%
    ## dplyr::select(idf.kw, emission.overall, energy.overall) %>%
    dplyr::left_join(prototype.area, by = "idf.kw") %>%
    dplyr::mutate(EUI.GJ.per.m2 =  energy.overall * 1e-9 / prototype.m2) %>%
    dplyr::mutate(emission.GJ.per.m2 =  emission.overall * 1e-9 / prototype.m2) %>%
    dplyr::select(idf.kw, epw.id, ends_with("per.m2")) %>%
    dplyr::mutate(heat.over.energy = emission.GJ.per.m2 / EUI.GJ.per.m2) %>%
    {.}

heat.eui.ratio.avg <- heat.eui.ratio %>%
    dplyr::group_by(idf.kw) %>%
    dplyr::summarise_if(is.numeric, mean) %>%
    dplyr::ungroup() %>%
    {.}

heat.eui.ratio.avg %>%
    dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
    na.omit() %>%
    ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                                 y = heat.over.energy,
                                 label = sprintf("%0.1f", heat.over.energy), fill=usetype)) +
    ggplot2::geom_bar(stat="identity") +
    ggplot2::coord_flip() +
    ggplot2::geom_hline(yintercept = 1.0) +
    ggplot2::ggtitle("Ratio of heat emission over energy consumption") +
    ggplot2::xlab("EnergyPlus input file") +
    ggplot2::ylab("heat emission divided by energy consumption") +
    ggplot2::scale_fill_manual(values = rev(RColorBrewer::brewer.pal(name="Paired", n=8))[c(1, 3, 5, 7)]) +
    ggplot2::guides(fill=ggplot2::guide_legend(nrow=2)) +
    ggplot2::ylim(c(0, 29)) +
    ggplot2::geom_text(hjust=-0.1) +
    ggplot2::theme(legend.position = "bottom")
ggplot2::ggsave(sprintf("../images/jul_heat_over_energy_ratio_prototype.png"), width = 9, height = 10)

```
