---
title: "Main analysis"
author: "Yujie Xu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)
knitr::opts_knit$set(root.dir = "~/Dropbox/workLBNL/EESA/AH_LA_AnalysisPaper/rmd/")
```

```{r helpers, message=FALSE}
library("dplyr")
library("tmap")
library("ggpmisc")
```

# Where does high heat emission come from

annual total heat emission in MJ/m2 of grid size

```{r loadData, fig.width = 10, fig.height = 10}
load("../AH.Analysis/data/df.finer.ann.rda")
load("../AH.Analysis/data/grid.finer.rda")
load("../AH.Analysis/data/la.boundary.valid.rda")

grid.finer.no.geo <- grid.finer

sf::st_geometry(grid.finer.no.geo) <- NULL

df.finer.ann.norm.area <- df.finer.ann %>%
  dplyr::left_join(grid.finer.no.geo, by = c("geoid"="id.grid.finer")) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:energy.overall) %>%
  dplyr::mutate(MJ.perm2.grid = GJ * 1e3 / area.m2) %>%
  dplyr::mutate(MJ.perm2.bldg.size = GJ * 1e3 / building.area.m2) %>%
  dplyr::mutate(MJ.perm2.bldg.foot = GJ * 1e3 / FootprintArea.m2) %>%
  dplyr::select(geoid, MJ.perm2.grid, MJ.perm2.bldg.size, MJ.perm2.bldg.foot) %>%
  dplyr::inner_join(grid.finer, by=c("geoid"="id.grid.finer")) %>%
  sf::st_as_sf() %>%
  {.}

tm_shape(df.finer.ann.norm.area) +
  tm_polygons(col="MJ.perm2.grid", title="Heat Emission (MJ/m2)", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_layout(main.title = "2018 Annual Heat Emission (MJ/m2 grid size)",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn"),
            title.size = 1) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)

## tm_shape(df.coarse.ann.norm.area) +
##   tm_polygons(col="MJ.perm2.grid", title="Heat Emission (MJ/m2)", n=10, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
##   tm_layout(main.title = "2018 Annual Heat Emission (MJ/m2 building footprint)",
##             legend.position=c("left", "bottom"), legend.outside=FALSE,
##             aes.palette = list(seq = "-RdYlGn")) +
##   tm_shape(la.boundary.valid) +
##   tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

# Which building type has the highest heat emission

Top heat emission building types in each grid

```{r HighEmissionType, fig.width = 10, fig.height = 10}

load("../AH.Analysis/data/annual.total.AH.per.usetype.grid.finer.rda")

highest.emission.type <- annual.total.AH.per.usetype.grid.finer %>%
  dplyr::arrange(id.grid.finer, desc(emission.overall)) %>%
  dplyr::group_by(id.grid.finer) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::inner_join(grid.finer, by=c("id.grid.finer")) %>%
  na.omit() %>%
  sf::st_as_sf() %>%
  {.}

tm_shape(highest.emission.type) +
  tmap::tm_polygons(col = "usetype", title = "Top heat emission building usetype", palette="Set3", border.alpha = 0) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

Dominant building type for each grid

```{r dominant building type, fig.width = 10, fig.height = 10}

load("../AH.Analysis/data/grid.finer.rda")

main.usetype.per.grid <- annual.total.AH.per.usetype.grid.finer %>%
  dplyr::select(id.grid.finer, usetype, building.area.m2) %>%
  dplyr::arrange(id.grid.finer, desc(building.area.m2)) %>%
  dplyr::group_by(id.grid.finer) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::left_join(grid.finer %>% dplyr::select(id.grid.finer), by = "id.grid.finer") %>%
  na.omit() %>%
  sf::st_as_sf() %>%
  {.}

tm_shape(main.usetype.per.grid) +
  tm_polygons(col="usetype", title="building use type", palette="Set3", border.alpha = 0) +
  tm_layout(main.title = "Dominant building type in each grid",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            title.size = 1) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```

Building type distribution for the top 10% heat emission grid cells.

```{r top10percentHeatEmissionGrid}
main.usetype.high.emission.grid <- df.finer.ann %>%
  dplyr::arrange(desc(emission.overall)) %>%
  dplyr::slice(1:(nrow(.) %/% 10)) %>%
  distinct(geoid) %>%
  dplyr::rename(id.grid.finer = geoid) %>%
  dplyr::inner_join(annual.total.AH.per.usetype.grid.finer, by = "id.grid.finer")  %>%
  dplyr::arrange(id.grid.finer, desc(building.area.m2)) %>%
  dplyr::group_by(id.grid.finer) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::left_join(grid.finer %>% dplyr::select(id.grid.finer), by = "id.grid.finer") %>%
  na.omit() %>%
  sf::st_as_sf() %>%
  {.}

tmap_mode("view")
tm_basemap("OpenStreetMap.Mapnik") +
tm_shape(main.usetype.high.emission.grid) +
  tm_polygons(col="usetype", title="building use type", palette="Set3", border.alpha = 0) +
  tm_layout(main.title = "Dominant building type in grid cells with high AH",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            title.size = 1) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)

annual.total.AH.per.usetype.grid.finer

to.reg <- annual.total.AH.per.usetype.grid.finer %>%
  dplyr::group_by(id.grid.finer) %>%
  dplyr::mutate(area.ratio = building.area.m2 / sum(building.area.m2)) %>%
  dplyr::ungroup() %>%
  dplyr::select(id.grid.finer, usetype, area.ratio) %>%
  tidyr::spread(usetype, area.ratio, fill = 0.0) %>%
  dplyr::inner_join(df.finer.ann %>%
                    dplyr::select(geoid, emission.overall),
                    by = c("id.grid.finer"="geoid")) %>%
  {.}

to.reg

reg.out <- lm(emission.overall ~ industrial + commercial + residential, data = to.reg)

reg.out
```

Prototype building annual heat emission

```{r prototypeBuildingAHandEnergy, fig.width = 10, fig.height = 10}
load("../AH.Analysis/data/ann.sim.result.by.idf.epw.rda")
load("../AH.Analysis/data/prototype.area.rda")
load("../AH.Analysis/data/idf.kw.to.usetype.rda")

annual.sim.EUI <- ann.sim.result.by.idf.epw %>%
  dplyr::select(idf.kw, epw.id, emission.overall, energy.overall) %>%
  tidyr::gather(variable, value, emission.overall:energy.overall) %>%
  dplyr::left_join(prototype.area, by = c("idf.kw")) %>%
  dplyr::mutate(GJ.per.m2 = value * 1e-9 / prototype.m2) %>%
  dplyr::select(-value, -prototype.m2) %>%
  {.}

annual.sim.EUI.avg <- annual.sim.EUI %>%
  dplyr::select(-epw.id) %>%
  dplyr::group_by(idf.kw, variable) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

annual.sim.EUI.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  dplyr::mutate_at(vars(variable), recode, "energy.overall"="Electricity + Gas GJ/m2",
                   "emission.overall"="Heat Emission GJ/m2") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, GJ.per.m2), y=GJ.per.m2, fill=interaction(variable, usetype))) +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ## ggplot2::scale_fill_grey(start=0.8, end=0.2) +
  ggplot2::scale_fill_brewer(palette = "Paired", direction=-1, name = "") +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=4)) +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("Annual heat emission or energy consumption (GJ/m2)") +
  ggplot2::ggtitle("Prototype building annual energy and heat emission") +
  ggplot2::coord_flip() +
  ggplot2::theme(legend.position = "bottom")

```

Prototype building annual heat emission to energy consumption ratio

```{r prototypeBuildingAhEnergyRatio, fig.width = 10, fig.height = 10}

heat.eui.ratio <- annual.sim.EUI %>%
  tidyr::spread(variable, GJ.per.m2) %>%
  dplyr::mutate(heat.over.energy = emission.overall / energy.overall) %>%
  {.}

heat.eui.ratio.avg <- heat.eui.ratio %>%
  dplyr::select(-epw.id) %>%
  dplyr::group_by(idf.kw) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

heat.eui.ratio.avg %>%
  dplyr::left_join(idf.kw.to.usetype, by="idf.kw") %>%
  ggplot2::ggplot(ggplot2::aes(x = reorder(idf.kw, heat.over.energy),
                               y = heat.over.energy,
                               label = sprintf("%0.1f", heat.over.energy), fill=usetype)) +
  ggplot2::geom_bar(stat="identity") +
  ggplot2::coord_flip() +
  ggplot2::geom_hline(yintercept = 1.0) +
  ggplot2::ggtitle("Ratio of heat emission over energy consumption") +
  ggplot2::xlab("EnergyPlus input file") +
  ggplot2::ylab("heat emission divided by energy consumption") +
  ggplot2::scale_fill_manual(values = rev(RColorBrewer::brewer.pal(name="Paired", n=8))[c(1, 3, 5, 7)]) +
  ggplot2::guides(fill=ggplot2::guide_legend(nrow=2)) +
  ggplot2::ylim(c(0, 16)) +
  ggplot2::geom_text(hjust=-0.1) +
  ggplot2::theme(legend.position = "bottom")
```

# Which AH component is the largest

## annual

```{r AHcomponent, fig.width = 10}

df.finer.ann %>%
  dplyr::select(-starts_with("energy"), -emission.overall) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:emission.surf) %>%
  ggplot2::ggplot(ggplot2::aes(x = variable, y = GJ, fill = variable)) +
  ggplot2::geom_boxplot() +
  ggplot2::ggtitle("Distribution of five AH component among finer grid") +
  ggplot2::coord_flip() +
  ggplot2::theme()

df.finer.ann %>%
  dplyr::select(-starts_with("energy"), -emission.overall) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:emission.surf) %>%
  ggplot2::ggplot(ggplot2::aes(x = variable, y = GJ, fill = variable)) +
  ggplot2::geom_boxplot() +
  ggplot2::ggtitle("Distribution of five AH component among finer grid, crop") +
  ggplot2::coord_flip(ylim = c(-1000, 40000)) +
  ggplot2::theme()
```

## monthly
```{r AHcomponentJuly, fig.width = 10, fig.height = 10}
load("../AH.Analysis/data/df.finer.month.rda")

df.finer.month %>%
  dplyr::select(-starts_with("energy"), -emission.overall) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:emission.surf) %>%
  ggplot2::ggplot(ggplot2::aes(x = variable, y = GJ, fill = variable)) +
  ggplot2::geom_boxplot() +
  ggplot2::ggtitle("Distribution of five AH component among finer grid") +
  ggplot2::facet_wrap(.~month, ncol = 2) +
  ggplot2::coord_flip() +
  ggplot2::theme()

df.finer.month %>%
  dplyr::select(-starts_with("energy"), -emission.overall) %>%
  tidyr::gather(variable, GJ, emission.exfiltration:emission.surf) %>%
  ggplot2::ggplot(ggplot2::aes(x = variable, y = GJ, fill = variable)) +
  ggplot2::geom_boxplot() +
  ggplot2::ggtitle("Distribution of five AH component among finer grid, crop") +
  ggplot2::facet_wrap(.~month, ncol = 2) +
  ggplot2::coord_flip(ylim = c(-5500, 7000)) +
  ggplot2::theme()
```

## Daily heat emission vs outdoor temperature

```{r dailyEmissionTemp, fig.width = 10}
load("../AH.Analysis/data/df.weather.2018.rda")

df.weather.avg <- df.weather.2018 %>%
  tidyr::gather(variable, value, DryBulb.C:`WindSpd.m/s`) %>%
  dplyr::group_by(month, day, hour, variable) %>%
  dplyr::summarise(value = mean(value)) %>%
  dplyr::ungroup() %>%
  {.}
df.weather.avg <- df.weather.avg %>%
  dplyr::select(-hour) %>%
  dplyr::group_by(month, day, variable) %>%
  dplyr::summarise_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  {.}

load("../AH.Analysis/data/df.finer.daily.rda")

grid.finer.area <- grid.finer

sf::st_geometry(grid.finer.area) <- NULL

grid.finer.area <- grid.finer.area %>%
  dplyr::select(id.grid.finer, area.m2) %>%
  tibble::as_tibble()

grid.finer.avg.wperm2 <- df.finer.daily %>%
  dplyr::left_join(grid.finer.area, by = c("geoid"="id.grid.finer")) %>%
  ## GJ to Wh, divide by 24h
  dplyr::mutate_at(vars(starts_with("emission"), starts_with("energy")), list(~ . * 277778 / 24 / .data$area.m2)) %>%
  dplyr::select(-geoid, -area.m2) %>%
  dplyr::group_by(date) %>%
  dplyr::summarize_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  tidyr::separate(date, into=c("month", "day"), sep="/") %>%
  dplyr::mutate_at(vars(month, day), as.numeric)

to.plot.correlation <- df.weather.avg %>%
  tidyr::spread(variable, value) %>%
  dplyr::inner_join(grid.finer.avg.wperm2, by=c("month", "day")) %>%
  {.}

to.plot.correlation %>%
  ggplot2::ggplot(ggplot2::aes(x = DryBulb.C, y=emission.overall)) +
  ggplot2::geom_point(size=0.5) +
  ggpmisc::stat_poly_line() +
  ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                          after_stat(rr.label), sep = "*\", \"*"))) +
  ggplot2::ylab("Average grid heat emission (W/m2)") +
  ggplot2::ggtitle("Daily average heat emission flux vs\noutdoor temperature") +
  ggplot2::theme(text = ggplot2::element_text(size = 20))

```


```{r dailyEmissionTempComp, fig.show="hold", out.width="50%", fig.width=6}
heat.source = c("emission.surf", "emission.rej", "emission.exfiltration", "emission.exhaust", "emission.ref")
heat.label = c("building surface", "HVAC rejection", "exfiltration", "exhaust",
               "relief air")
for (i in seq_along(heat.source)) {
  p <- to.plot.correlation %>%
    ggplot2::ggplot(ggplot2::aes_string(x = "DryBulb.C", y=heat.source[[i]])) +
    ggplot2::geom_point(size=0.5) +
    ggpmisc::stat_poly_line() +
    ggpmisc::stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                            after_stat(rr.label), sep = "*\", \"*"))) +
    ggplot2::xlab("DryBulb Temperature") +
    ggplot2::ylab("Average grid heat emission (W/m2)") +
    ggplot2::ggtitle(sprintf("Daily average %s heat emission flux vs\noutdoor temperature", heat.label[[i]])) +
    ggplot2::theme(text = ggplot2::element_text(size = 14),
                   axis.title = ggplot2::element_text(size = 14))
  print(p)
}
```

# The timing of highest heat emission

## monthly total

```{r monthlyTotal, fig.show="hold", out.width="50%", fig.width=6, fig.height=4}
to.plot.monthly <- df.finer.month %>%
  dplyr::left_join(grid.finer.area, by = c("geoid"="id.grid.finer")) %>%
  ## MJ/m2, normalized by grid cell area, roughly 200,000m2
  dplyr::mutate_at(vars(starts_with("emission"), starts_with("energy")), list(~ . * 1e3 / .data$area.m2)) %>%
  dplyr::select(-geoid, -area.m2) %>%
  dplyr::group_by(month) %>%
  dplyr::summarize_if(is.numeric, mean) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(month = as.numeric(month)) %>%
  {.}

to.plot.monthly %>%
  ggplot2::ggplot(ggplot2::aes(x = month, y = emission.overall)) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::scale_x_continuous(breaks=1:12) +
  ggplot2::ggtitle("Monthly Total Heat Emission Averaged Across 450m Grids") +
  ggplot2::theme()

to.plot.monthly %>%
  dplyr::select(-emission.overall) %>%
  dplyr::select(month, starts_with("emission")) %>%
  tidyr::gather(variable, value, starts_with("emission")) %>%
  ggplot2::ggplot(ggplot2::aes(x = month, y = value, color = variable)) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::scale_x_continuous(breaks=1:12) +
  ggplot2::ggtitle("Monthly Total Heat Emission by Component Averaged Across 450m Grids") +
  ggplot2::theme()
```

## diurnal profile overall and by month

```{r diurnalPerMonth, fig.width=7, fig.height=4}
load("../AH.Analysis/data/diurnal.month.finer.rda")
load("../AH.Analysis/data/diurnal.finer.rda")

diurnal.finer %>%
  ggplot2::ggplot(ggplot2::aes(x = hour, y = emission.overall)) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::scale_x_continuous(breaks=0:23) +
  ggplot2::ggtitle("Hourly Average Heat Emission Averaged Across 450m Grids") +
  ggplot2::theme()

label.hr = 13
df.label <- diurnal.month.finer %>%
  dplyr::filter(hour == label.hr) %>%
  {.}

diurnal.month.finer %>%
  dplyr::mutate(month = factor(month)) %>%
  ggplot2::ggplot() +
  ggplot2::geom_point(ggplot2::aes(x=hour, y=emission.overall, color=month)) +
  ggplot2::geom_line(ggplot2::aes(x=hour, y=emission.overall, color=month), linetype="dashed") +
  ggrepel::geom_label_repel(ggplot2::aes(x=label.hr, y=emission.overall, label=month), data=df.label) +
  ggplot2::geom_line(ggplot2::aes(x=hour, y=emission.overall), data=diurnal.finer) +
  ggplot2::geom_point(ggplot2::aes(x=hour, y=emission.overall), data=diurnal.finer) +
  ggplot2::ylab("Heat Emission (W/m2)") +
  ggplot2::ggtitle("Diurnal total building AH profile by month") +
  ggplot2::theme()
```

```{r diurnalPerMonthComponent, fig.show="hold", out.width="50%"}
for (i in seq_along(heat.source)) {
  variable = heat.source[[i]]
  p <- diurnal.month.finer %>%
    dplyr::mutate(month = factor(month)) %>%
    ggplot2::ggplot() +
    ggplot2::geom_point(ggplot2::aes_string(x="hour", y=variable, color="month")) +
    ggplot2::geom_line(ggplot2::aes_string(x="hour", y=variable, color="month"), linetype="dashed") +
    ggrepel::geom_label_repel(ggplot2::aes_string(x=label.hr, y=variable, label="month"), data=df.label) +
    ggplot2::geom_line(ggplot2::aes_string(x="hour", y=variable), data=diurnal.finer) +
    ggplot2::geom_point(ggplot2::aes_string(x="hour", y=variable), data=diurnal.finer) +
    ggplot2::ylab("Heat Emission (W/m2)") +
    ggplot2::ggtitle(sprintf("Diurnal %s heat emission profile by month", heat.label[[i]])) +
    ggplot2::theme()
  print(p)
}
```

# Comparison of the spatial distribution of heat emission at noon and night in a weekday and a weekend day in winter and summer

```{r mapSnapshot, fig.width = 10}
load("../AH.Analysis/data/snapshot.finer.rda")

to.plot.snapshot <- snapshot.finer %>%
  dplyr::left_join(grid.finer %>% dplyr::select(id.grid.finer),
                   by=c("geoid"="id.grid.finer")) %>%
  sf::st_as_sf() %>%
  {.}

tmap_mode("plot")
tm_shape(to.plot.snapshot) +
  tm_polygons(col="emission.overall", n=8, style="quantile", midpoint=0, palette="seq", border.alpha = 0) +
  tm_facets(by="time.label", ncol=4) +
  tm_layout(main.title = "Heat emission at different time snapshots",
            legend.position=c("left", "bottom"), legend.outside=FALSE,
            aes.palette = list(seq = "-RdYlGn")) +
  tm_shape(la.boundary.valid) +
  tm_polygons("CITY", alpha=0, legend.show=FALSE)
```
